---
title: "DATA 605 Assignment 8"
author: "Warner Alexis"
date: "2024-03-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Week Assignment 8 

1) 1. Let X1, X2, . . . , Xn be n mutually independent random variables, each of
which is uniformly distributed on the integers from 1 to k. Let Y denote the
minimum of the Xi’s. Find the distribution of Y .

# Solution 

The probabiblity that any single $X_i$ is greater that y $\frac {k-y}{k}$, so $k-y$ is greater than y out of total of k.

$P(Y = y) = (\frac {k-y}{k})^n - (\frac {k-(y+1)}{k})^n $

for $y = 1,2,...,k$.

Y is the minimum of $X_1,X_2...X_n$ where $X_i$ is uniformly distributed. 


2) Your organization owns a copier (future lawyers, etc.) or MRI (future doctors). This machine has a manufacturer’s expected lifetime of 10 years. This means that we expect one failure every ten years. (Include the probability statements and R Code for each part.).

```{r}
# Probability of Success 
p <- 9/10

# Probability the mission will fail after 8 years 
fail_prob <- 1 - p^8 
cat("Probability the machine will fail after 8 years", fail_prob,"\n")

#Expected value 
cat("The expected value is ", 1/p,"\n")

# Standard Deviation 
cat("The Standard deviation is ", sqrt((1-p)/(p^2)),"\n")


```
b) b. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as an exponential. 

```{r}
# rate of lambda 
lambda <- 1/10

cat("The probability that the machine will fail " , exp(-lambda * 8), "\n")

cat("The expected value", 1/ lambda,"\n")

cat("The standar deviation is: ", 1/ lambda,"\n")
```
C) What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as a binomial. (Hint: 0 success in 8 years) 


The  probability that there is 0 failure after 8 years. 
$P(X=8) = \sum_{0}^n\dbinom{n}{k}(1-p)^n-k$

Asumming $p = 1/10$ and $n=8$

```{r}
# probability of success 
p <- 1/10
#number of years
n <- 8 

# the number of failure 
# number of failures in first 8 years
failures <- 0

cat("Probaility that machine will face after 8 years",pbinom(failures,n,p),"\n")


    
```


d) What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as a Poisson. 


Let calculate the probability that the machine will fail after 8 years. 
$P(X=8) = \sum_{0}^n\dbinom{8}{0}\frac {\lambda^x_e-\lambda}{x!}$

```{r}
lambda <- 1

cat("The probability that the machine will fail after 8 years: ", 1 - ppois(7, lambda*8),"\n")

# Expected Value
cat("The Expected Value is: ", lambda * 8, "\n")

# Standard Deviation 
cat("The Standard Deviation is ", sqrt(lambda * 8),"\n")
```

